{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-09-05 wacv_for_review.tex
Final Replies to Comments

We, first, use two hand-crafted features, fHoG \cite{felzenszwalb2010object} 
and color-naming \cite{li2014scale} in the {\it E}nKCF as shown in Figure~\ref{fig:Filters}. 
This version of {\it E}nKCF is dedicated to perform tracking on any embedded systems at
$30$ fps.

In particular, the translation filter, $R_{t}^{L}$, uses
both the fHoG \cite{felzenszwalb2010object} and color-naming
\cite{van2009learning} features to learn the large background area
around the target as shown in Figure~\ref{fig:Filters}.b. The color features 
compensate for the noisier fHoG features due to the large ROI considered 
by $R_{t}^{L}$. {\it Burak: You meant ``the
  color features are used to compensate for shape features' weakness
  -- what's weakness?}

  {\it YoungWoo : The weakness is the more background you include the noisier
  HoG features become.}
On the other hand, the color features is not assigned to the small area translation 
filter,  $R_{t}^{S}$, as it learns more useful fHoG features than $R_{t}^{L}$ due to smaller
padding size as seen in Figure~\ref{fig:Filters}.a. {\it Burak: color features are not used for $R_{t}^{S}$ because?
\it YoungWoo : We do not use color features because  $R_{t}^{S}$ concentrates on smaller ROI
than  $R_{t}^{L}$}. Finally, both fHoG and color-naming features are used for $R_{s}$, the scale filter, 
since the lower template resolution (64 x n)
assigned to $R_{s}$ leads to less discriminative shape
features as in Figure~\ref{fig:Filters}.c. Smaller template size is assigned to $R_{s}$ as it estimates
the scale by correlating the filter with multiple ROIs as shown in
alg.~\ref{alg:MKCF}.  This way, we can keep the run-time complexity of
the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. By doing so, we can avoid
fluctuating run-time performance among KCFs which is not desired in embedded
systems.

@@

There has been a large volume of studies on utilizing a pre-trained
CNN features to tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer of the VGGNet \cite{simonyan2014very}
for this idea where their experiments showed that the
first convolutional layer features lead to slightly better precision
and success rates than the second layer. \cite{ma2015hierarchical}
proposed a KCF tracker integrating features with higher abstraction capacity. 
Their method first employs the third convolutional layer features to estimate the response map. In
the next stage, they used the estimation of the target's transition
from the first phase to use the second convolutional layer features
and update transition estimation.  Finally, the first convolutional
layer features is extracted from the ROI estimated in the second
stage. This coarse-to-fine approach accommodates
different levels of abstractions of the object. However, such approach
runs multiple KCFs at a single frame, increasing the run-time
complexity. For this reason, we follow a similar approach to
\cite{danelljan2015convolutional} to embed deep features in {\it
  E}nKCF.

Our {\it E}nKCF framework allows us to exploit different level of
feature encodings with different KCFs. The translation filters,
$R_{t}^{L}$ and $R_{t}^{S}$, considers at least twice bigger area than
the scale filter, $R_{s}$. Taking this into account, we can assign deeper feature
encodings to $R_{s}$ as it learns less spatial information than
$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
the second layer features ($109\times109\times64$). This feature
assignment scheme is represented as \textit{conv224-VGG} and shown in
fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. We use the VGGNet as it provides higher spatial
resolution at the first several layers than AlexNet
\cite{krizhevsky2012imagenet}.

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
{\it Burak: We cannot just begin with a detail. You need to give the
  readers an overview of what they'll be reading.}

In this section, we evaluate the performance of the proposed {\it E}nKCF
tracker and its variants on the object tracking benchmarks. 
In this direction, we choose two publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects.
We first evaluate the performance of {\it E}nKCF 
with hand-crafted features.  With this tracker, we aim
at developing an object tracking algorithm that ``efficiently'' runs
on an embedded system, a drone, for example, in ``high speed,'' $\ge
300$ fps. Given this, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset for comparison. To this end, we chose the OTB100 dataset that
contains the videos recorded from smart phones and typical cameras in
perspective view. Lastly, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, called
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets.

@@

%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm on any existing embedded systems
for real-world applications is economically and practically very
attractive. To make such pipelines more plausible, however, those
algorithms should run faster with small footprint of computation
resource consumption. To make an object tracking algorithm meet these
practical requirements, we proposed an extension of KCF that
essentially deploys three KCFs, in turn, to address the scale change
and dynamic maneuvers of a target. The way we ran three KCFs is
optimal in a sense that efficiently handled the scale change and
effectively learned the translation of the target. We also developed a
Bayes filter, particle filter, to smooth the transition between three
KCFs. In particular, the particle filter estimated the target's pixel
coordinates using information about the target's motion observed over
frames. We used two publicly available dataset to evaluate the
performance of the proposed algorithm and found, on average, the
performance of the proposed algorithm is better than those of the
existing ones over 5\% on precision at 20 pixels and 10-20\% on AUC on
average. Our implementation ran at 340 fps for OTB100 and at 416 fps
for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
(292 fps), DCF (457 fps) for UAV123. Finally, we represented objects with deep
feature encodings to boost tracking performance by about $5\%$ on embedded systems with GPUs. 
To further improve the performance, we employed deeper features to the scale filter as it learns smaller ROI
than the translation filters.

>>>>

We, first, use two complimentary hand-crafted features, fHoG (shape) \cite{felzenszwalb2010object} 
and color-naming (color) \cite{li2014scale} in the {\it E}nKCF as shown in Figure~\ref{fig:Filters}. 
This version of {\it E}nKCF is dedicated to perform tracking on any embedded systems at
$30$ fps, particularly on the ones without GPU units.

In particular, the translation filter, $R_{t}^{L}$, employs
both the fHoG \cite{felzenszwalb2010object} and color-naming
\cite{van2009learning} features to learn the large background area
around the target as shown in Figure~\ref{fig:Filters}.b. The color features 
compensate for the noisier fHoG features due to the large background area considered 
by $R_{t}^{L}$. {\it Burak: You meant ``the
  color features are used to compensate for shape features' weakness
  -- what's weakness?}

  {\it YoungWoo : The weakness is the more background you include the noisier
  HoG features become.}
On the other hand, the color features is not assigned to the small area translation 
filter,  $R_{t}^{S}$, as it learns more useful fHoG features than $R_{t}^{L}$ due to smaller
padding size as seen in Figure~\ref{fig:Filters}.a. {\it Burak: color features are not used for $R_{t}^{S}$ because?
\it YoungWoo : We do not use color features because  $R_{t}^{S}$ concentrates on smaller ROI
than  $R_{t}^{L}$}. Finally, both fHoG and color-naming features are used in the scale filter, $R_{s}$, 
since the ROI is resized to a lower template resolution (64 x n) than the translation filters. This leads to 
less discriminative shape features as in Figure~\ref{fig:Filters}.c. The $R_{s}$ estimates
the scale by correlating the filter with multiple ROIs as shown in
alg.~\ref{alg:MKCF}.  This introduces additional operations in the frames $R_{s}$ is used. To reduce the 
number of operations, we assign a smaller template size to $R_{s}$. This does not degrade the tracking performance
due to two major reasons: (1) zero padding size and (2) integration of color features.
This way, we keep the run-time complexity of
the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. By doing so, fluctuating run-time performances among KCFs are avoided which is
desired in embedded systems.

@@

There has been a large volume of studies on utilizing a pre-trained
CNN features to tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer of the VGGNet \cite{simonyan2014very}.
They report that the first convolutional layer features lead to slightly better precision
and success rates than the second layer due to lost spatial information this layer. \cite{ma2015hierarchical}
proposed a KCF tracker integrating features with higher abstraction capacity. 
Their method first employs the third convolutional layer features to estimate the response map. In
the next stage, the KCF, concentrating on the second convolutional layer features, is run to update
transition. The third KCF then works on the transition given by the previous KCF and learns the first convolutional
layer features to update the transition. This coarse-to-fine approach accommodates
different levels of abstractions of the object. However, it
runs multiple KCFs in a sequential fashion, increasing the run-time
complexity. For this reason, we follow a similar approach to
\cite{danelljan2015convolutional} to embed deep features in {\it
  E}nKCF.

Our {\it E}nKCF framework allows us to exploit different level of
feature encodings with different KCFs. The translation filters,
$R_{t}^{L}$ and $R_{t}^{S}$, consider at least twice bigger area than
the scale filter, $R_{s}$. Taking this into account, we can assign deeper feature
encodings to $R_{s}$ as it learns less spatial information than
$R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the
fourth convolutional layer features ($26\times26\times128$) to $R_{s}$
whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of
the second layer features ($109\times109\times64$). This feature
assignment scheme is represented as \textit{conv224-VGG} and shown in
fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. We use the VGGNet since it provides higher spatial
resolution at the first several layers than AlexNet
\cite{krizhevsky2012imagenet}.

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
In this section, we evaluate the performance of the proposed {\it E}nKCF
tracker and its variants on the object tracking benchmarks. 
In this direction, we choose two publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects.
We first evaluate the performance of {\it E}nKCF 
with hand-crafted features as shown in Figure~\ref{fig:Filters}.  
With this tracker, we aim at developing an object tracking algorithm that ``efficiently'' runs
on an embedded system, a drone, for example, in ``high speed,'' $\ge
300$ fps. Given this, we believe that the UAV123 dataset is a good fit in
evaluating the performance of the proposed algorithm. In addition, in
the UAV123 dataset, there are many challenging, realistic scenes, e.g.,
abrupt scale/illumination changes. Although we are primarily
interested in developing an algorithm for mobile, embedded robotic
applications, it is also important to compare the performance of the
proposed algorithm with those of the state-of-the-art in a nominal
dataset for comparison. To this end, we chose the OTB100 dataset that
contains the videos recorded from smart phones and typical cameras in
perspective view. Lastly, we tested the proposed algorithm on a
temporally down-sampled version of the UAV123 dataset, called
UAV123$\_$10fps dataset. What we would like to evaluate using this
modified dataset is how robust the proposed algorithm is to the
drastic motions of camera and targets.

@@

%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm on any existing embedded systems
for real-world applications is economically and practically very
attractive. To make such pipelines more plausible, however, those
algorithms should run faster with small footprint of computation
resource consumption. To make an object tracking algorithm meet these
practical requirements, we proposed an extension of KCF that
essentially deploys three KCFs, in turn, to address the scale change
and dynamic maneuvers of a target. The way we ran three KCFs is
optimal in a sense that efficiently handled the scale change and
effectively learned the translation of the target. We also developed a
Bayes filter, particle filter, to smooth the transition between three
KCFs. In particular, the particle filter estimated the target's pixel
coordinates using information about the target's motion observed over
frames. We used two publicly available dataset to evaluate the
performance of the proposed algorithm and found, on average, the
performance of the proposed algorithm is better than those of the
existing ones over 5\% on precision at 20 pixels and 10-20\% on AUC on
average. Our implementation ran at 340 fps for OTB100 and at 416 fps
for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
(292 fps), DCF (457 fps) for UAV123. Finally, we represented objects with deep
feature encodings to boost tracking performance by about $5\%$ on embedded systems with GPUs. 
To further improve the performance, we employed deeper features in the scale filter since it has zero
padding around the target.
